Extending the WebID Protocol with Access Delegation

### 2012-08-04 paper.tex
remove todos
fix abstract

\begin{abstract}
The WebID protocol enables the global identification of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
But in order for such a server to decide whether access should be granted or denied to a particular WebID, the web server may need to retrieve other profiles and linked resources to work out e.g. if the requesting agent is member of an authorized group (e.g. is a friend of a friend (FOAF) of the resource owner).
If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
In this paper we explore different ways how an agent can act as a user as well as we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g. allowing a server to be able to act on behalf of its users.
This extends the range of application scenarios where WebID authentication can be efficiently deployed while increasing privacy.
\end{abstract}

@@

Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
This could require $N$ parallel connections to the same server $S$. 
Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetrick key cryptographic handshake. 
For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
organisations may be a serious drawback.
%\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
\todo{ST: add disadvantages according to the requirements (identity)}

>>>>

\begin{abstract}
The WebID protocol enables the global identification and authentication of agents in a distributed manner by combining asymmetric cryptography and Linked Data.
But in order to decide whether access should be granted or denied to a particular WebID, the authenticating web server may need to retrieve other profiles and linked resources to work out e.g. if the requesting agent is member of an authorized group.
If these linked resources (e.g. FOAF profiles) are required to be publicly available for the server to access it, then this would be a major privacy limitation on a linked Social Network.
In this paper we explore different ways how an agent can act as a user as well as we propose an extension to the WebID protocol which allows for delegation of access authorization from a WebID to a third party, e.g. allowing a server to be able to act on behalf of its users.
This extends the range of application scenarios where WebID authentication can be efficiently deployed while increasing privacy.
\end{abstract}

@@

Secondly, whenever the Origin Server needs to act as $U_1$ to a remote server $R$ it will need to open a new TLS connection to that server using the certificate $C_{u1}$ for that user.
This could require $N$ parallel connections to the same server $S$. 
Opening TLS connections is somewhat expensive: it requires opening up a new TCP connection and starting an expensive asymmetrick key cryptographic handshake. 
For small numbers of N this can be defended, but as N becomes large the inefficiency this could create between two
organisations may be a serious drawback.
%\todo{calculate how inefficient this is, and at what size of network this starts really become problematic}
%\todo{ST: add disadvantages according to the requirements (identity)}
